Robust positively invariant sets for state dependent and scaled disturbances

### 2015-03-23 draft.tex
Corrected typo in referencing.
Labled pictures in tex for consistency.
checked changes and added notes

by~\eqref{eq:PWA:distrubance:set} with a convex piecewise affine $H(x)$.

@@

keep growing. It might be confusing with the notation but that is only to emphasise that it behaves like the inverse..}

@@

\note{This looks very MATLAB.. I don't like it.}

@@

equation $\dot x = f(x,u)$ around an equilibrium point $(\hat x, \hat u)$ gives the approximate model 

@@

	 \dot{\tilde{x}} \approx \underbrace{\left(\begin{array}{cc}

@@

      u)}\tilde x 

@@

      u)}\tilde u

@@

\note{I find the $x^+\approx Ax+Bu$ notation very misleading! I prefer $=$ since we 
will take it as an equality after all not handling discretisation errors at all..}
where $\tilde{x} = x-\hat{x}$, $\tilde{u} = u -\hat{u}$.

@@

\tilde{x}^+ \approx A \tilde{x} + B \tilde{u}, \quad

@@

@@

and the linearisation around $(\hat{x},\hat{u})$, we obtain the successor state:

@@

t\tilde u) dt\cdot \tilde u \\

@@

             + t\tilde u)dt - A \Bigr)\tilde x 

@@

&\quad +\Bigl(\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u + t\tilde u)dt - B\Bigr)\tilde u

@@

\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u, 

@@

Suppose that for all $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact sets,
we can bound the values of $H^x x+ H^u u$ by a finite convex combination of extremal values, i.e. 
$H^x x+H^u u\in\conv_k\{H^x_k x + H^u_k u\}$.

@@

extremal values.. That's obviously not the case..}

@@

\mathcal V(x,u)=\biggl\{v:\min_k\{
H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge 

@@

v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}, \, i =1,\dots,n\biggr\}.

@@

\abs{\hat x_1-x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{\hat u-u}\leq10mA\}$.

@@

which is less conservative than using fixed bounds on the nonlinearities as we will see in the next example.

@@

$\alpha_3$ and is blown up by normalising.}

@@

\centerline{\includegraphics[scale=0.6]{twoDimensional}}

@@

\centerline{\includegraphics[scale=0.6]{threeDimensional}}

>>>>

by~\eqref{eq:PWA:disturbance:set} with a convex piecewise affine $H(x)$.

@@

keep growing. It might be confusing with the notation but that is only
to emphasise that it behaves like the inverse [change notation, e.g.
$\Psi^\dagger$?]}

@@

\note{This looks very MATLAB.. I don't like it [saves space]}

@@

equation $\dot x = f(x,u)$ around an equilibrium point $(\hat x, \hat
u)$ gives the approximate linear model 

@@

	 \Delta\dot{x} = \underbrace{\left(\begin{array}{cc}

@@

      u)}\Delta x 

@@

      u)}\Delta u

@@

\note{I find the $x^+\approx Ax+Bu$ notation very misleading! I prefer
  $=$ since we will take it as an equality after all not handling
  discretisation errors at all.. [OK - agreed]}
where $\Delta u = u -\hat{u}$ and $\Delta x \approx x-\hat{x}$.

@@

\Delta x^+ = A \Delta x + B \Delta u , \quad

@@

\note{What is $w$ here?}

@@

and the linearisation around $(\hat{x},\hat{u})$, and defining 
$\tilde{x} = x - \hat{x}$, $\tilde{u} = u - \hat{u}$ we obtain the successor state:

@@

t\tilde{u}) dt\cdot \tilde{u} \\

@@

             + t\tilde{u})dt - A \Bigr)\tilde x 

@@

&\quad +\Bigl(\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x +
  t\tilde x,\hat u + t\tilde{u})dt - B\Bigr)\tilde{u}

@@

\tilde x^+ = A\tilde x+B\tilde{u} + H^x\tilde{x} + H^u \tilde{u}, 

@@

Suppose that for all $x\in\mathcal X$ and $u\in\mathcal U$, where
$\mathcal X$ and $\mathcal U$ are compact sets, $f(x,u)$ is
continuously differentiable. Then
we can bound the values of $H^x \tilde{x}+ H^u \tilde{u}$ by a finite convex combination of extremal values, i.e. 
$H^x \tilde{x}+H^u \tilde{u}\in\conv_k\{H^x_k \tilde{x} + H^u_k \tilde{u}\}$.

@@

extremal values.. That's obviously not the case.. [We can assume this
if $f$ is continuously differentiable]}

@@

\mathcal V(\tilde{x},\tilde{u})=\biggl\{v:\min_k\{
H^x_{k,i}\tilde{x}+H^u_{k,i}\tilde{u}\}\leq v_i\,\wedge 

@@

v_i \leq \max_k\{H^x_{k,i}\tilde{x}+H^u_{k,i}\tilde{u}\}, \, i =1,\dots,n\biggr\}.

@@

\abs{x_1- \hat x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{ u-\hat u}\leq10mA\}$.

@@

which is less conservative than using fixed bounds on the
nonlinearities as we will see in Section~\ref{sec:second:example}.

@@

$\alpha_3$ and is blown up by normalising. [some comment is needed in
the text]}

@@

\begin{lpic}{twoDimensional(.6,)}
\lbl[r]{4,9;$-3$}
\lbl[r]{4,22;$-2$}
\lbl[r]{4,35;$-1$}
\lbl[r]{4,49;$0$}
\lbl[r]{4,62;$1$}
\lbl[r]{4,76;$2$}
\lbl[r]{4,89;$3$}
\lbl[t]{6,3;$-10$}
\lbl[t]{17,3;$-8$}
\lbl[t]{28,3;$-6$}
\lbl[t]{39,3;$-4$}
\lbl[t]{50,3;$-2$}
\lbl[t]{63,3;$0$}
\lbl[t]{74,3;$2$}
\lbl[t]{85,3;$4$}
\lbl[t]{96,3;$6$}
\lbl[t]{107,3;$8$}
\lbl[t]{118,3;$10$}
{\footnotesize
\lbl[r]{0,52,90;$x_2$}
\lbl[t]{63,0;$x_1$}

@@

\begin{lpic}{threeDimensional(.6,)}
\lbl[r]{4,69;$6$}
\lbl[r]{4,61;$5$}
\lbl[r]{4,53;$4$}
\lbl[r]{4,45;$3$}
\lbl[r]{4,37;$2$}
\lbl[r]{4,29;$1$}
\lbl[r]{4,21;$0$}
\lbl[r]{4,13;$-1$}
\lbl{9,5;$6$}
\lbl{24,5;$4$}
\lbl{40,4;$2$}
\lbl{55,4;$0$}
\lbl{69,3;$-2$}
\lbl{83,3;$-4$}
\lbl{99,3;$-6$}
\lbl{116,8;$-10$}
\lbl{120,16;$0$}
\lbl{126,23;$10$}
{\footnotesize
\lbl{125,15;$x_1$}
\lbl{50,2;$x_2$}
\lbl[r]{-1,40,90;$\theta$}
